NumPy---Array Programming in Python

### 2020-02-20 body.tex
Make all captions sentences

% KJM: I moved this here to get the placement right
% FIXME SJW: let's review caption (d); I don't think it's crystal clear what
% we're trying to show there; double check caption (g)
\begin{figure*}[h]
  \centering
  \includegraphics[width=\textwidth]{static/sketches/concepts}
  \caption{\textbf{Fundamental Array Concepts.}
    \textbf{a,} The NumPy array data structure and its associated metadata fields.
    \textbf{b,} Indexing an array with slices and steps. These
  operations return a \emph{view} of the original data.
    \textbf{c,} Indexing an array with masks, scalar coordinates, or
  other arrays, so that it returns a copy of the original data. In the
  bottom example, an array is indexed with other arrays; this broadcasts the indexing arguments before performing the lookup.
    \textbf{d,} Vectorization efficiently applies operations to groups
  of elements.
    \textbf{e,} Broadcasting in the multiplication of two-dimensional arrays.
    \textbf{f,} Reduction operations act along one or more axes. In this
    example, an array is be summed along various axes to produce a vector, or along two axes consecutively to
    produce a scalar.
    \textbf{g,} Example NumPy code, illustrating some of these concepts.
   }
  \label{fig:array-concepts}
\end{figure*}

@@

  \caption{\textbf{NumPy API and Array Protocols.} Through its array protocols, the NumPy API
     can operate on various types of array objects, including those written outside
     of NumPy. In this example, NumPy's \code{mean} function is called on a Dask
     array.  The call succeeds by dispatching to the appropriate library implementation
     (i.e., Dask in this case) and results in a new Dask array.  Compare this
     code to the example code in Fig.~\ref{fig:array-concepts}g.
  }\label{fig:array-protocol}

>>>>

% KJM: I moved this here to get the placement right
% FIXME SJW: let's review caption (d); I don't think it's crystal clear what
% we're trying to show there; double check caption (g)
\begin{figure*}[h]
  \centering
  \includegraphics[width=\textwidth]{static/sketches/concepts}
  \caption{\textbf{The NumPy array incorporates several fundamental array concepts.}
    \textbf{a,} The NumPy array data structure and its associated metadata fields.
    \textbf{b,} Indexing an array with slices and steps. These
  operations return a \emph{view} of the original data.
    \textbf{c,} Indexing an array with masks, scalar coordinates, or
  other arrays, so that it returns a copy of the original data. In the
  bottom example, an array is indexed with other arrays; this broadcasts the indexing arguments before performing the lookup.
    \textbf{d,} Vectorization efficiently applies operations to groups
  of elements.
    \textbf{e,} Broadcasting in the multiplication of two-dimensional arrays.
    \textbf{f,} Reduction operations act along one or more axes. In this
    example, an array is be summed along various axes to produce a vector, or along two axes consecutively to
    produce a scalar.
    \textbf{g,} Example NumPy code, illustrating some of these concepts.
   }
  \label{fig:array-concepts}
\end{figure*}

@@

  \caption{\textbf{NumPy's API and array protocols expose new arrays to the ecosystem.}
     In this example, NumPy's \code{mean} function is called on a Dask
     array.  The call succeeds by dispatching to the appropriate library implementation
     (i.e., Dask in this case) and results in a new Dask array.  Compare this
     code to the example code in Fig.~\ref{fig:array-concepts}g.
  }\label{fig:array-protocol}
